\begin{thebibliography}{99}

\renewcommand{\baselinestretch}{1} 
\small

\bibitem{iot_exp}
\textit{Internet of Things is a revolutionary approach for future technology enhancement: a review}
\\\url{https://journalofbigdata.springeropen.com/articles/10.1186/s40537-019-0268-2}

\bibitem{iot_sec}
\textit{A roadmap for security challenges in the Internet of Things}
\\\url{https://doi.org/10.1016/j.dcan.2017.04.003}

\bibitem{mac_atk}
\textit{Analysis on Manipulation of the MAC Address and Consequent Security Threats}
\\\url{https://doi.org/10.1145/2995959.2995975}

\bibitem{deeplearningbook} 
\textit{Deep Learning}
\\Ian Goodfellow and Yoshua Bengio and Aaron Courville, 2016, MIT Press
\\\url{http://www.deeplearningbook.org}

\bibitem{deep_method}
\textit{A Short Review of Deep Learning Methods for Understanding Group and Crowd Activities}
\\\url{https://ieeexplore.ieee.org/document/8489692}

\bibitem{deep_audio}
\textit{Deep Learning for Audio Signal Processing}
\\\url{https://arxiv.org/abs/1905.00078}

\bibitem{computer_vision1}
\textit{Deep Learning for Computer Vision: A Brief Review}
\\\url{https://doi.org/10.1155/2018/7068349}

\bibitem{computer_vision2}
\textit{Deep Learning vs. Traditional Computer Vision}
\\\url{https://arxiv.org/pdf/1910.13796.pdf}



\bibitem{perceptron}
\textit{The perceptron: a probabilistic model for information storage and organization in the brain}
\\\url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.335.3398}

\bibitem{nielsen}
\textit{Neural Networks and Deep Learning}
\\\url{http://neuralnetworksanddeeplearning.com}

\bibitem{relu}
\textit{Deep Learning using Rectified Linear Units (ReLU)}
\\\url{https://arxiv.org/pdf/1803.08375.pdf}

\bibitem{elu}
\textit{Fast and Accurate Deep Network Learning by Exponential Linear Units (ELUs)}
\\\url{https://arxiv.org/abs/1511.07289}

\bibitem{gelu}
\textit{Gaussian Error Linear Units (GELUS)}
\\\url{https://arxiv.org/pdf/1606.08415.pdf}

\bibitem{pca}
\textit{Principal component analysis: a review and recent developments}
\\\url{https://doi.org/10.1098/rsta.2015.0202}




\bibitem{lossfunc}
\textit{On Loss Functions for Deep Neural Networks
in Classification}
\\\url{https://arxiv.org/pdf/1702.05659.pdf}

\bibitem{kullbackeff}
\textit{Optimism in Reinforcement Learning and Kullback-Leibler Divergence
}
\\\url{https://arxiv.org/abs/1004.5229}

\bibitem{kullbackeff2}
\textit{Why Deep Learning Methods Use KL Divergence
Instead of Least Squares: A Possible Pedagogical
Explanation}
\\\url{https://scholarworks.utep.edu/cgi/viewcontent.cgi?article=2188&context=cs_techrep}



\bibitem{overfitting}
\textit{An Overview of Overfitting and its Solutions}
\\\url{https://arxiv.org/pdf/1609.04747.pdf}


\bibitem{backprop}
\textit{An Overview of Overfitting and its Solutions}
\\\url{Learning representations by back-propagation errors}

\bibitem{var_grad}
\textit{An overview of gradient descent optimization
algorithms}
\\\url{Learning representations by back-propagation errors}

\bibitem{adam}
\textit{Adam: A Method for Stochastic Optimization}
\\\url{https://arxiv.org/abs/1412.6980}

\bibitem{bert}
\textit{BERT: Pre-training of Deep Bidirectional Transformers for
Language Understanding}
\\\url{https://arxiv.org/pdf/1810.04805.pdf}

\bibitem{gpt}
\textit{Language Models are Unsupervised Multitask Learners}
\\\url{https://cdn.openai.com/better-language-models/language_models_are_unsupervised_multitask_learners.pdf}



\bibitem{reg_gen}
\textit{Regularization for Deep Learning: A Taxonomy}
\\\url{https://arxiv.org/abs/1710.10686}


\bibitem{l1reg}
\textit{L1 regularization is better than L2 for learning and predicting chaotic systems
}
\\\url{https://arxiv.org/pdf/cs/0410015.pdf}

\bibitem{l2reg}
\textit{$L_2$ Regularization for Learning Kernels}
\\\url{https://arxiv.org/pdf/1205.2653.pdf}

\bibitem{srivastava}
\textit{Dropout: A Simple Way to Prevent Neural Networks from Overfitting}
\\\url{http://jmlr.org/papers/volume15/srivastava14a/srivastava14a.pdf}


\bibitem{webfingerprint1}
\textit{The Web never forgets: Persistent tracking mechanisms in the wild}
\\\texttt{Proc. ACM SIGSAC Conf. Comput. Commun. Secur. Secur., pp. 674-689}

\bibitem{webfingerprint2}
\textit{FPDetective: Dusting the web for fingerprinters}
\\\texttt{Proc. ACM SIGSAC Conf. Comput. Commun. Secur., pp. 1129-1140}

\bibitem{radiofingerprint}
\textit{Wireless device identification with radiometric signatures}
\\\texttt{Proc. ACM SIGSAC Conf. Comput. Commun. Secur., pp. 1129-1140}

\bibitem{idos1}
\textit{Passive OS fingerprinting by DNS traffic analysiss}
\\\url{https://ieeexplore.ieee.org/document/6531762}

\bibitem{idos2}
\textit{Study on OS fingerprinting and nat/tethering based on DNS log analysis}
\\\url{https://irtf.org/raim-2015-papers/raim-2015-paper21.pdf}


\bibitem{iot_2020}
\textit{How the ’Internet of Things’ will impact consumers,
businesses, and governments in 2016 and beyond.}
\\\url{http://www.businessinsider.de/how-the-internet-of-things-market-will-grow-2014-10}

\bibitem{attk1}
\textit{AVTECH DVR multiple vulnerabilities.}
\\\url{https://www.coresecurity.com/core-labs/advisories/avtech-dvr-multiple-vulnerabilities}

\bibitem{attk2}
\textit{Hacking a Wi-Fi coffee machine – part 1.}
\\\url{https://www.pentestpartners.com/security-blog/hacking-a-wi-fi-coffee-machine-part-1/}

\bibitem{flaw}
\textit{400,000 publicly available IoT devices vulnerable to single
flaw.}
\\\url{https://blog.senr.io/blog/400000-publicly-available-iot-devices-vulnerable-to-single-flaw}

\bibitem{clasf}
\textit{Supervised machine learning: a review of classification techniques.}
\\\url{https://dl.acm.org/doi/10.5555/1566770.1566773}

\bibitem{imbclasf}
\textit{Survey on deep learning with class imbalance.}
\\\url{https://journalofbigdata.springeropen.com/articles/10.1186/s40537-019-0192-5}


\bibitem{4sics_site}
\textit{Capture files from 4SICS Geek Lounge}
\\\url{https://www.netresec.com/?page=PCAP4SICS}

\bibitem{iot_site}
\textit{IoT devices captures. Aalto University}
\\\url{https://research.aalto.fi/en/datasets/iot-devices-captures}

\bibitem{iot_paper}
\textit{IOT SENTINEL: Automated Device-Type
Identification for Security Enforcement in IoT}
\\\url{https://arxiv.org/pdf/1611.04880.pdf}

\bibitem{python}
\textsc{Python 3} Documentation
\\\url{https://docs.python.org/3/}

\bibitem{numpy}
\textsc{Numpy} Documentation
\\\url{https://numpy.org/doc/}

\bibitem{pandas}
\textsc{Pandas} Documentation
\\\url{https://pandas.pydata.org/docs/}

\bibitem{wireshark}
\textsc{Wireshark} Documentation
\\\url{https://www.wireshark.org/download/docs/user-guide.pdf}

\bibitem{data_aug}
\textit{Time Series Data Augmentation for Deep Learning: A Survey}
\\\url{https://arxiv.org/pdf/2002.12478.pdf}



\bibitem{gce}
\textit{Nozomi Networks Guardian Community Edition}
\\\url{https://community.nozominetworks.com/}

\bibitem{nozomi}
\textsc{Nozomi Networks} website
\\\url{https://www.nozominetworks.com/}

 
\bibitem{tf} 
\textsc{TensorFlow} Documentation 
\\\url{https://www.tensorflow.org/guide}

\bibitem{keras} 
\textsc{Keras} Documentation 
\\\url{https://keras.io/}

\bibitem{auc} 
\textit{The use of the area under the ROC curve in the evaluation of machine learning algorithms}
\\\url{https://doi.org/10.1016/S0031-3203(96)00142-2}

\bibitem{auc_var} 
\textit{A critical analysis of variants of the AUC}
\\\url{https://link.springer.com/content/pdf/10.1007/s10994-008-5070-x.pdf}







\end{thebibliography}
